MacLeish

### 2016-03-30 README.Rmd

The Ada and Archibald MacLeish Field Station is a 260-acre patchwork of forest and farmland located in West Whately, MA that provides opportunities for faculty and students to pursue environmental research, outdoor education, and low-impact recreation. Reid Bertone-Johnson serves as the Field Station Manager and five faculty and staff sit on the field station's Advisory Board.  More information can be found at (http://www.smith.edu/ceeds/macleish.php)

>>>>

The Ada and Archibald MacLeish Field Station is a 240-acre patchwork of forest and farmland located in West Whately, MA that provides opportunities for faculty and students to pursue environmental research, outdoor education, and low-impact recreation. Reid Bertone-Johnson serves as the Field Station Manager and five faculty and staff sit on the field station's Advisory Board.  More information can be found at (http://www.smith.edu/ceeds/macleish.php)
